\chapter{Abstract}
\label{abstract}

Cloud storage is an essential aspect of modern computing,
enabling users to store and access data globally.
It is being used by individuals, businesses, and organizations for various applications,
including file sharing, data backup, and collaboration.

Alternative to cloud storage, we have decentralized storage systems,
which focus especially on privacy, security, censorship resistance, but not so much on data integrity.
Cloud storage is already employing various techniques to monitor and ensure data integrity,
such as checksums, error correction codes, and replication.
Due to the decentralized nature of decentralized storage systems,
these techniques may not be directly applicable,
as they are more susceptible to attacks and undesirable behaviors from the network's participants.

This thesis aims to design and implement a secure and fault-tolerant decentralized storage system that can rival centralized solutions.
Specifically, it focuses on addressing the integrity of data stored in decentralized networks,
a critical issue not fully resolved by existing systems.
The proposed system will operate on peer-to-peer (P2P) networks,
leveraging structured network topologies such as Kademlia,
to ensure efficient routing and resource discovery.

The primary contribution of this work is the development of a storage system with
an integrity verification mechanism that ensures data consistency and reliability,
mitigating the risk of data corruption and loss.
This involves evaluating proof of retrievability (PoR) techniques and a reputation system based on a ledger to combat malicious nodes.
The system's scalability, performance, resilience, reliability, availability,
and security are also considered to ensure comprehensive evaluation and testing.

\vfill
